### 2019-08-22 maciek.tex
Omega(kl)

  To this end, we inspect the sequences $v^{C}_i$ for each cluster, and select the cluster $C'$ whose node $v^{C'}_{k-2}$, i.e., the penultimate node appears last in the sequence $\langle x^{(i)}\rangle$, and we end the sequence $I_2'$ just before its appearance.
  Then, we set $d^{(1)} = v^{C'}_{k-2}$, $d^{(2)} = v^{C'}_{k-1}$.
  Such choice guarantees that requests from $I_2'$ are free for OPT.
  Furthermore, the number of requests of $I_2'$ is at least $|I_2| - \ell - 1$: as $D$ is the last cluster to remain with two singleton clusters, all other $\ell-1$ clusters have at most $1$ singleton cluster.

  Finally, OPT pays $2$, and DET pays $L - \ell - 1 = \Omega(\ell \cdot k)$.

>>>>

  To this end, we inspect the sequences $v^{C}_i$ for each cluster, and select such the cluster $D$ whose node $v^{D}_{k-2}$, i.e., the penultimate node appears last in the sequence $\langle x^{(i)}\rangle$, and we end the sequence $I_2'$ just before its appearance.
  Then, we set $d^{(1)} = v^{D}_{k-2}$ and $d^{(2)} = v^{D}_{k-1}$.
  Such choice guarantees that requests from $I_2'$ are free for OPT.
  Furthermore, the number of requests of $I_2'$ is at least $|I_2| - \ell - 1$: as $D$ is the last cluster to remain with two singleton clusters, all other $\ell-1$ clusters have at most $1$ singleton cluster.

  We conclude that for the input $I_1I_2'$ OPT pays $2$, and DET pays $L - \ell - 1 = \Omega(\ell \cdot k)$.
